Lessons learned: creating tutorials to teach agent-based modelling to archaeologists

### 2025-08-26 paper.Rmd
minor corrections

```{r, screenshot-lesson-3, echo = FALSE, out.width="100%", fig.cap = "Screenshot of lesson 3 in tutorial 1 showing the population dynamics of the Long House Valley in the Artificial Anasazi model created by Axtell et al. (2002)."}
knitr::include_graphics("paper_files/ScreenshotABMAtutorial1lesson3.png")
```

@@

```{r workshop-impression, echo = FALSE, out.width="100%", fig.cap = "Impression of various workshops (CAA 2023 in Amsterdam and EAA 2023 in Belfast) with participants working."}
knitr::include_graphics("paper_files/CollageWorkshops.jpg")
```

@@

This project was undertaken with the support of the Erasmus+ programme of the European Union (<https://erasmus-plus.ec.europa.eu/nl/projects/search/details/2021-2-IE01-KA220-VET-000049054>). The publication was financed by The Carlsberg Foundation's *Young Researcher Fellowship* (CF21-0382); IR was supported by the European Union's Horizon 2020 Research and Innovation Programme under the Marie Skłodowska-Curie grant agreement no 754513, the Aarhus University Research Foundation and FWO grant number W001220N.

>>>>

```{r, screenshot-lesson-3, echo = FALSE, out.width="100%", fig.cap = "Screenshot of lesson 3 in tutorial 1 showing the population dynamics of the Long House Valley in the Artificial Anasazi model created by Axtell et al. (2002)."}
knitr::include_graphics("figures/ScreenshotABMAtutorial1lesson3.png")
```

@@

```{r workshop-impression, echo = FALSE, out.width="100%", fig.cap = "Impression of various workshops (CAA 2023 in Amsterdam and EAA 2023 in Belfast) with participants working."}
knitr::include_graphics("figures/CollageWorkshops.jpg")
```

@@

This project was undertaken with the support of the Erasmus+ programme of the European Union (<https://erasmus-plus.ec.europa.eu/nl/projects/search/details/2021-2-IE01-KA220-VET-000049054>). The Past Social Networks Project was funded by The Carlsberg Foundation's Young Researcher Fellowship (CF21-0382) awarded to Tom Brughmans. Iza Romanowska was supported by the European Union's Horizon 2020 Research and Innovation Programme under the Marie Skłodowska-Curie grant agreement no 754513, the Aarhus University Research Foundation and FWO grant number W001220N.

### 2025-08-26 paper.tex
minor corrections

\title{Lessons learned: creating tutorials to teach agent-based modelling to archaeologists}
\author{}
\date{\vspace{-2.5em}July 24, 2025}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{paper_files/ScreenshotABMAtutorial1lesson3} \caption{Screenshot of lesson 3 in tutorial 1 showing the population dynamics of the Long House Valley in the Artificial Anasazi model created by Axtell et al. (2002).}\label{fig:screenshot-lesson-3}
\end{figure}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{paper_files/CollageWorkshops} \caption{Impression of various workshops (CAA 2023 in Amsterdam and EAA 2023 in Belfast) with participants working.}\label{fig:workshop-impression}
\end{figure}

@@

This project was undertaken with the support of the Erasmus+ programme of the European Union (\url{https://erasmus-plus.ec.europa.eu/nl/projects/search/details/2021-2-IE01-KA220-VET-000049054}). The publication was financed by The Carlsberg Foundation's \emph{Young Researcher Fellowship} (CF21-0382); IR was supported by the European Union's Horizon 2020 Research and Innovation Programme under the Marie Skłodowska-Curie grant agreement no 754513, the Aarhus University Research Foundation and FWO grant number W001220N.

>>>>

\title{Lessons learned: creating tutorials to teach agent-based modelling to archaeologists}
\author{}
\date{\vspace{-2.5em}August 26, 2025}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{figures/ScreenshotABMAtutorial1lesson3} \caption{Screenshot of lesson 3 in tutorial 1 showing the population dynamics of the Long House Valley in the Artificial Anasazi model created by Axtell et al. (2002).}\label{fig:screenshot-lesson-3}
\end{figure}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{figures/CollageWorkshops} \caption{Impression of various workshops (CAA 2023 in Amsterdam and EAA 2023 in Belfast) with participants working.}\label{fig:workshop-impression}
\end{figure}

@@

This project was undertaken with the support of the Erasmus+ programme of the European Union (\url{https://erasmus-plus.ec.europa.eu/nl/projects/search/details/2021-2-IE01-KA220-VET-000049054}). The Past Social Networks Project was funded by The Carlsberg Foundation's Young Researcher Fellowship (CF21-0382) awarded to Tom Brughmans. Iza Romanowska was supported by the European Union's Horizon 2020 Research and Innovation Programme under the Marie Skłodowska-Curie grant agreement no 754513, the Aarhus University Research Foundation and FWO grant number W001220N.
